---
title: "Experiment"
author: "Rodrigo Valdes Ortiz"
date: "4/23/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

```{r}
# General issues
blank_theme <- theme_minimal()+
  theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.border = element_blank(),
  panel.grid=element_blank(),
  axis.ticks = element_blank(),
  plot.title=element_text(size=14, face="bold")
  )
```

```{r}
# Function to create  pie
pie_function <- function(df, order, color_baseline, flavor) {
  
  # Factor (the first thing is the input, the order is in the second)
  df$flavor <- factor(df$flavor, flavor[order])
  color_array <- color_baseline[order]
  
  bp <- ggplot(df, aes(x="", y=number, fill = flavor)) + 
    geom_bar(width = 1, stat = "identity")

  pie <- bp + coord_polar("y", start=0)

  pie +  
    blank_theme + theme(axis.text.x=element_blank()) + 
    scale_fill_manual(values= color_array)
}
```

# 5. Sum of slices
Question: Which proportion of customers buy chocolate or vanilla?

Intuition: the distance among two slices might affect the ability to sum quantities

```{r}
order_1 = c(1,2,3,4,5,6)
order_2 = c(1,3,2,4,5,6)
order_3 = c(1,3,4,2,5,6)
order_4 = c(1,3,4,5,2,6)
order_5 = c(1,3,4,5,6,2)

color_baseline = c("lightgoldenrodyellow", "chocolate4", "brown2", "yellow2", "darkorange2", "navy")
```

## 5.1 Sample 1: similar slice size
```{r}
flavor <- c('vanilla','chocolate','strawberry', 'lemon', 'peach', 'blueberry')
# number <- c(10, 20, 18, 22, 30)
number <- c(9, 16, 20, 24, 18, 13)
five_df <- data.frame(flavor, number)

pie_function(five_df, order_1, color_baseline, flavor)
pie_function(five_df, order_2, color_baseline, flavor)
pie_function(five_df, order_3, color_baseline, flavor)
pie_function(five_df, order_4, color_baseline, flavor)
pie_function(five_df, order_5, color_baseline, flavor)
```
## 5.2 Sample 2: different slice sizes
```{r}
# number <- c(5,8,12,47,28)
number <- c(6, 13, 24, 8, 31, 18)
five_df_2 <- data.frame(flavor, number)

pie_function(five_df_2, order_1, color_baseline, flavor)
pie_function(five_df_2, order_2, color_baseline, flavor)
pie_function(five_df_2, order_3, color_baseline, flavor)
pie_function(five_df_2, order_4, color_baseline, flavor)
pie_function(five_df_2, order_5, color_baseline, flavor)

```

# 6. Prior ideas about colors might change perception
Question: Which is the proportion of customers who buy vanilla?

Intuition: Ideas about the correctness of color labeling might affect comprehension

## 6.1 Only the color of the question is wrong
```{r}
flavor <- c('vanilla','chocolate','strawberry', 'lemon', 'peach', 'blueberry')
number <- c(9, 16, 20, 24, 18, 13)

six_df <- data.frame(flavor, number)
color_baseline_six = c("paleturquoise1", "chocolate4", "brown2", "yellow2", "darkorange2", "navy")

pie_function(six_df, order_1, color_baseline_six, flavor)

```

## 6.2 Only the color of question is right
```{r}
color_baseline_six_3 = c("lightgoldenrodyellow", "navy", "chocolate4", "brown2", "yellow2", "darkorange2")

pie_function(six_df, order_1, color_baseline_six_3, flavor)
```

## 6.3 All colors are wrong
```{r}
color_baseline_six_2 = c("chocolate4", "lightgoldenrodyellow", "navy", "brown2", "yellow2", "darkorange2")

pie_function(six_df, order_1, color_baseline_six_2, flavor)
```





